### 2025-05-07 paper/abs_en.tex
feat: polish15

In the process of modern agriculture’s transformation towards intelligence, precision harvesting has become a key factor in improving agricultural production efficiency and quality. Among these, the weighing of fruits and vegetables during harvest is an essential part of precision harvesting. With the widespread application of electronic scales, their role in fruit and vegetable harvesting on smart farms has become increasingly prominent. However, at present, fruit and vegetable harvesting still largely depends on manual operations, making the accurate recording of harvested fruits’ weights and the scientific management of fruit yields particularly urgent.

Against this backdrop, this research conducts an in-depth survey of agricultural production activities, applying software engineering principles to identify and analyze specific requirements. It utilizes various software technologies, including web development techniques and YOLO-based fruit and vegetable recognition technologies, to design and develop a cloud-based agricultural fruit weighing software. This software achieves stable and high-performance data processing capabilities, provides efficient and rich information management functions, and offers multi-dimensional data visualization. Finally, the software’s various functionalities were tested, and performance tests on key interfaces were conducted in specific hardware environments, demonstrating the core indicators of the software to meet the deployment needs in practical production environments.

In conclusion, the cloud-based agricultural fruit weighing software developed in this study provides an efficient, stable, and feature-rich solution for smart farm fruit harvesting and weighing management, contributing to the advancement of precision harvesting and digital management in smart farms.

>>>>

As modern agriculture undergoes a transformation toward intelligent systems, the precise collection of fruit weighing data has become a critical foundation for efficient management and informed decision-making. However, traditional weighing often suffer from delayed data recording, frequent manual intervention, and poor hardware compatibility, which significantly hinder the efficiency and reliability of agricultural yield statistics.

To address these limitations, this study proposes and implements a cloud-based software system for agricultural fruit weighing that integrates multi-protocol communication, image recognition, and cloud data management. The system adopts a collaborative architecture between edge and remote nodes, ensuring independent data processing at both ends. At the edge, the system captures real-time fruit images and weight data, identifies fruit types using YOLO-based image recognition, and publishes weighing messages. The remote server subscribes to weighing data reported by the electronic scale and performs subsequent data processing and storage. The software supports multiple communication protocols such as MQTT, HTTP, and CoAP, enabling compatibility with various weighing devices for flexible integration and rapid deployment. A data management and visualization platform was developed using Spring Boot and Vue, offering efficient data management capabilities and multidimensional visualization of collected data. Comprehensive functional and performance tests were conducted under specific hardware environments, demonstrating the system’s ability to meet deployment requirements in real-world agricultural settings.

In conclusion, the proposed cloud-based fruit weighing software provides an efficient, robust, and feature-rich solution for intelligent fruit weighing and data management in smart farms, thereby facilitating precise harvesting and advancing the digital transformation of agriculture.

### 2025-05-07 paper/abs_zh.tex
feat: polish15

在现代农业向智慧化转型的进程中，精准收获成为提升农业生产效率与质量的关键环节。其中，果蔬采摘的称重工作是精准收获的重要组成部分。随着电子秤的广泛推广应用，其在智慧农场果蔬采摘中的作用日益凸显。然而，目前果蔬采摘很大程度上依赖人工操作，这就使得对采摘果实进行准确的称重记录以及对果实产量进行科学管理的需求变得尤为迫切。

基于以上背景，本研究深入调研农业生产活动，应用软件工程相关知识理论，归纳与分析具体需求，利用包括WEB开发技术、基于YOLO的果实识别技术等在内的软件技术，设计并开发农业果实称重云端软件。通过该软件实现了稳定且高性能的数据处理能力，提供了高效且丰富的信息管理功能以及多个维度下数据的可视化。此外，研究还进一步完成了对软件各项功能的测试以及在特定硬件环境下针对多个关键功能的性能测试，展现软件各项核心指标，以满足实际生产环境下软件的部署需求。

综上所述，本研究实现的农业果实称重云端软件为智慧农场的果实采摘称重管理提供了一个高效、稳定且功能丰富的解决方案，有助于推动智慧农场的精准收获和数字化管理。

>>>>

在现代农业向智慧化转型的进程中，果实称重信息的精准采集成为实现高效管理与智能决策的重要基础。传统的称重流程中存在数据记录滞后、人工干预频繁、设备兼容性差等问题，严重影响了农业产量统计的效率与可靠性。

为解决上述瓶颈，本文提出并实现了一套融合多协议通信、图像识别与云端数据管理的农业果实称重云端软件。软件的整体架构采用远边端协同的模式进行设计，实现了两端数据处理的独立性。农场边端实时采集果实图像与重量信息，使用基于 YOLO 的图像识别技术识别出果实种类，最后发布称重消息。远端订阅电子秤上报的称重消息，完成后续的数据处理与存储。软件支持通过 MQTT、HTTP、CoAP 等多种通信协议发布称重消息，适配多类型称重硬件，可实现灵活接入与快速部署。软件使用 Spring Boot + Vue 技术构建农场数据管理与可视化平台，提供了高效且丰富的信息管理功能以及多个维度下数据的可视化。研究完成了对软件各项功能的测试以及在特定硬件环境下针对多个关键功能的性能测试，展现软件各项核心指标，以满足实际生产环境下软件的部署需求。

综上所述，本研究实现的农业果实称重云端软件为智慧农场的果实称重和数据管理提供了一个高效、稳定且功能丰富的解决方案，有助于推动智慧农场的精准收获和数字化管理。
